opponent modelling

### 2020-01-15 Experiment_2/exp2_clean_analysis.Rmd
finalise v1 of report

@@

```{r}
# AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
citation(package = "afex", lib.loc = NULL, auto = NULL)
library(afex)
a1 <- aov_car(int_score ~ game.f*interaction_lvl*condition.f*opp_type + Error(human_id/(game.f*interaction_lvl*opp_type)), dat_int)
summary(a1)
(a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),
  observed = attr(a1$anova_table, "observed"),
  correction = attr(a1$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(a1$anova_table,
  "p_adjust_method"), sig_symbols = attr(a1$anova_table, "sig_symbols")))

>>>>

write.csv(dat, file = "dat_exp2.csv")
write.csv(dat_int, file = "dat_int_exp2.csv")
```

@@

```{r}
# AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
#citation(package = "afex", lib.loc = NULL, auto = NULL)
library(afex)
a1 <- aov_car(int_score ~ game.f*interaction_lvl*condition.f*opp_type + Error(human_id/(game.f*interaction_lvl*opp_type)), dat_int)
summary(a1)

(a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),
  observed = attr(a1$anova_table, "observed"),
  correction = attr(a1$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(a1$anova_table,
  "p_adjust_method"), sig_symbols = attr(a1$anova_table, "sig_symbols")))
